\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{array}
\usepackage{geometry}

\geometry{top=20pt, bottom=20pt, left=20pt, right=20pt}

\title{Linear Optimization Set 1}
\author{Student Name: Erla Priyanka}
\date{Student ID: 1606063}
\begin{document}

\maketitle

\Question*{1. Maximizing Profit for Motor Oil Production}

\subsubsection*{1. Component Data}
\begin{tabular}{|c|c|c|}
\hline
\textbf{Component} & \textbf{Max Barrels/day} & \textbf{Cost/Barrel} \\
\hline
1 & 4500 & \$12 \\
2 & 2700 & \$10 \\
3 & 3500 & \$14 \\
\hline
\end{tabular}

\subsubsection*{2. Grade Specifications and Selling Price}
\begin{tabular}{|c|c|c|}
\hline
\textbf{Grade} & \textbf{Specifications} & \textbf{Selling Price/Barrel} \\
\hline
Super & $\geq$ 50\% of Component 1 & \$23 \\
 & $\leq$ 30\% of Component 2 & \\
Premium & $\geq$ 40\% of Component 1 & \$20 \\
 & $\leq$ 25\% of Component 3 & \\
Extra & $\geq$ 60\% of Component 1 & \$18 \\
 & $\geq$ 10\% of Component 2 & \\
\hline
\end{tabular}

\subsubsection*{3. Constraints}
\begin{itemize}
    \item The total amount of Component 1 across all grades should not exceed 4500 barrels.
    \item The total amount of Component 2 across all grades should not exceed 2700 barrels.
    \item The total amount of Component 3 across all grades should not exceed 3500 barrels.
    \item Each grade of oil should not exceed 3000 barrels.
\end{itemize}

\subsection*{ Decision Variables}
\noindent Let the following variables represent the amount of each component used in each grade:
\begin{itemize}
    \item \( x_{1S}, x_{2S}, x_{3S} \): Amount of Components 1, 2, and 3 in Super grade.
    \item \( x_{1P}, x_{2P}, x_{3P} \): Amount of Components 1, 2, and 3 in Premium grade.
    \item \( x_{1E}, x_{2E}, x_{3E} \): Amount of Components 1, 2, and 3 in Extra grade.
\end{itemize}

\subsection*{ Constraints}

\subsubsection*{1. Component Constraints:}
\begin{align*}
x_{1S} + x_{1P} + x_{1E} &\leq 4500 \\
x_{2S} + x_{2P} + x_{2E} &\leq 2700 \\
x_{3S} + x_{3P} + x_{3E} &\leq 3500
\end{align*}

\subsubsection*{2. Grade Specifications:}
\begin{itemize}
    \item \textbf{Super:}
    \begin{align*}
    x_{1S} &\geq 0.5(x_{1S} + x_{2S} + x_{3S}) \\
    x_{2S} &\leq 0.3(x_{1S} + x_{2S} + x_{3S})
    \end{align*}
    \item \textbf{Premium:}
    \begin{align*}
    x_{1P} &\geq 0.4(x_{1P} + x_{2P} + x_{3P}) \\
    x_{3P} &\leq 0.25(x_{1P} + x_{2P} + x_{3P})
    \end{align*}
    \item \textbf{Extra:}
    \begin{align*}
    x_{1E} &\geq 0.6(x_{1E} + x_{2E} + x_{3E}) \\
    x_{2E} &\geq 0.1(x_{1E} + x_{2E} + x_{3E})
    \end{align*}
\end{itemize}

\subsubsection*{3. Production Limits:}
\begin{align*}
x_{1S} + x_{2S} + x_{3S} &\leq 3000 \\
x_{1P} + x_{2P} + x_{3P} &\leq 3000 \\
x_{1E} + x_{2E} + x_{3E} &\leq 3000
\end{align*}

\subsection*{Step 4:  Objective Function}
\noindent  maximum profit \( Z \) :
\[
Z = [23(x_{1S} + x_{2S} + x_{3S}) + 20(x_{1P} + x_{2P} + x_{3P}) + 18(x_{1E} + x_{2E} + x_{3E})] - [12(x_{1S} + x_{1P} + x_{1E}) + 10(x_{2S} + x_{2P} + x_{2E}) + 14(x_{3S} + x_{3P} + x_{3E})]
\]

\begin{tabular}{|c|c|c|c|}
\hline
\textbf{Grade} & \textbf{Component 1} & \textbf{Component 2} & \textbf{Component 3} \\
\hline
Super & 1500 & 300 & 200 \\
Premium & 1200 & 500 & 300 \\
Extra & 1800 & 200 & 400 \\
\hline
\end{tabular}

\subsection*{Maximum Profit after optimization with solver}
\$18,400 per day.

\vspace{290pt}
\newpage
\Question*{2. Make or Buy? Maximizing Profit for HDD and SSD Production}

\subsection*{Objective}
Determine the optimal number of Hard Disk Drives (HDD) and Solid State Drives (SSD) to fabricate in-house and purchase from a subcontractor to maximize profit.

\subsection*{Decision Variables}
Let:
\begin{itemize}
    \item \( x_{H,in} \) = Number of HDDs fabricated in-house.
    \item \( x_{S,in} \) = Number of SSDs fabricated in-house.
    \item \( x_{H,out} \) = Number of HDDs purchased from the subcontractor.
    \item \( x_{S,out} \) = Number of SSDs purchased from the subcontractor.
\end{itemize}

\subsection*{Objective Function}
Maximize profit \( Z \):
\[
Z = [(82 - 75)x_{H,in} + (125 - 117)x_{S,in} + (82 - 79)x_{H,out} + (125 - 123)x_{S,out}]
\]

\subsection*{Constraints}

\begin{enumerate}
    \item \textbf{Demand Satisfaction:}
    \begin{align*}
    x_{H,in} + x_{H,out} &\geq 2215 \text{ (HDD demand)} \\
    x_{S,in} + x_{S,out} &\geq 1512 \text{ (SSD demand)} \\
    x_{H,in} + x_{S,in} &\leq 2282 \text{ (Total HDD+SSD production limit)}
    \end{align*}
    
    \item \textbf{Production Capacity:}
    \begin{align*}
    0.1x_{H,in} + 0.12x_{S,in} &\leq 350 \text{ (Fabrication)} \\
    0.15x_{H,in} + 0.11x_{S,in} &\leq 230 \text{ (Assembly)} \\
    0.13x_{H,in} + 0.13x_{S,in} &\leq 450 \text{ (Shipping)}
    \end{align*}
\end{enumerate}

\subsection*{Solution }

\begin{enumerate}
    \item \textbf{Linear Program:}
    \begin{itemize}
        \item Objective Function: \( Z \)
        \item Constraints: Demand Satisfaction, Production Capacity
    \end{itemize}
    
    \item \textbf{Optimization:}
    \begin{itemize}
        \item Using Solver to determine  optimal values for \( x_{H,in}, x_{S,in}, x_{H,out}, x_{S,out} \).
    \end{itemize}
\end{enumerate}

\subsection*{Optimized Solution}
Optimal Production (units per month):

\begin{tabular}{|c|c|c|}
\hline
 & HDD & SSD \\
\hline
In-house & 424.53 & 1512 \\
Subcontracted & 345.47 & 0 \\
\hline
\end{tabular}

\subsection*{Maximum Profit}
\$16,104.13 per month.

\vspace{290pt}
\end{document}
